Supplemental Materials for ``Universals of word order result from optimization of grammars for efficient communication''

### 2019-01-19 writeup/pnas-word-order-si.tex
rewiring correlations analysis

    \includegraphics[scale=.25]{../results/correlations/coverage-langmod-best.pdf}
    \includegraphics[scale=.25]{../results/correlations/coverage-parse-best.pdf}
    \includegraphics[scale=.25]{../results/correlations/coverage-two-lambda09-best.pdf}

    \includegraphics[scale=.25]{../results/correlations/coverage-ground.pdf}
    \includegraphics[scale=.25]{../results/correlations/coverage-depl.pdf}
	\caption{Correlations satisfied by the best word order grammars for predictability, parseability, efficiency, by the UD languages, and by the best grammars for dependency length.}
    \label{fig:posterior-prevalence}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.7]{../results/correlations/posterior_joint_with_ud.pdf}
	\caption{Posteriors of the prevalences of the correlations among languages optimized for Predictability (red), parseability (green), and efficiency (blue), controlling for languages and language families, with prevalence in the UD languages.}
    \label{fig:posterior-prevalence}
\end{figure}

>>>>

    \includegraphics[scale=.25]{../results/correlations/figures/coverage-langmod-best.pdf}
    \includegraphics[scale=.25]{../results/correlations/figures/coverage-parse-best.pdf}
    \includegraphics[scale=.25]{../results/correlations/figures/coverage-two-lambda09-best.pdf}

    \includegraphics[scale=.25]{../results/correlations/figures/coverage-ground.pdf}
    \includegraphics[scale=.25]{../results/correlations/figures/coverage-depl.pdf}
	\caption{Correlations satisfied by the best word order grammars for predictability, parseability, efficiency, by the UD languages, and by the best grammars for dependency length.}
    \label{fig:posterior-prevalence}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.7]{../results/correlations/figures/posterior_joint_with_ud.pdf}
	\caption{Posteriors of the prevalences of the correlations among languages optimized for Predictability (red), parseability (green), and efficiency (blue), controlling for languages and language families, with prevalence in the UD languages.}
    \label{fig:posterior-prevalence}
\end{figure}
